%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.7in}
\addtolength{\evensidemargin}{-0.7in}
\addtolength{\textwidth}{1.4in}
\addtolength{\topmargin}{-0.6in}
\addtolength{\textheight}{1.2in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]



% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Large \scshape Dhaivat Pachchigar} \\ \vspace{1pt}
    \small 909-670-8973 $|$ \href{dhaivatpachchigar@gmail.com}{\underline{dhaivatpachchigar@gmail.com}} $|$ 
    \href{https://www.linkedin.com/in/dhaivat-pachchigar-b58493242/}{\underline{linkedin.com/in/Dev}}
     $|$
    \href{https://github.com/devPach4545}{\underline{GitHub Profile}}
    
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of California, San Diego}{La Jolla, CA}
      {Bachelor of Science, Computer Science \textbf{GPA: 3.7 }(Regents Scholar)}{September 2022 -- June 2025}
   
  \resumeSubHeadingListEnd

    
%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Full Stack -  Task Manager} $|$ \emph{ Next.js, SpringBoot, Mysql, Material-UI, Tailwind CSS, Redux, Junit }}
          
          \resumeItemListStart
          
           \resumeItem{Engineered a full-stack task management web app using \textbf{React} for the frontend and \textbf{Spring Boot} for the backend, allowing admins to assign tasks to users and users to submit their tasks}
           \resumeItem{Employed a \textbf{microservices architecture} to separate \textbf{User}, \textbf{Task}, and \textbf{Submission} functionalities.}
            \resumeItem{Applied \textbf{Redux Toolkit} for efficient \textbf{state management} and integrated \textbf{Thunk} as middleware to streamline data handling between components using \textbf{Eureka Server}}
            \resumeItem{Implemented task features, including creation, assignment, updating, deletion, and filtering, to enhance task management capabilities. }
            \resumeItem{Utilized \textbf{MySQL} for data storage and management, ensuring reliable data retrieval and consistency.}
            
            \resumeItem{Secured the application with \textbf{JWT authentication} and \textbf{role-based permissions} to safeguard user data and maintain access control.}

          \resumeItemListEnd
          
    


        \resumeProjectHeading
{\textbf{Full Stack - Social Media Website} $|$ \emph{React.Js, Java, Spring Boot, MySQL, Material-UI, Redux, Tailwind CSS, JUnit}}

\resumeItemListStart
  \resumeItem{Built a comprehensive \textbf{full-stack web application} using \textbf{React} for the frontend and \textbf{Spring Boot} for the backend.}
  \resumeItem{Integrated \textbf{ Redux} as a \textbf{state management system} and \textbf{Thunk} as \textbf{middleware} to ensure seamless data flow and optimized performance.}
  \resumeItem{Developed and integrated features such as user account creation, post creation, and designed functionality for commenting and liking posts.}
  \resumeItem{Devised\textbf{ real-time chat functionality} using \textbf{WebSocket} technology to enhance user experience.}
  \resumeItem{Designed \textbf{JWT-based authentication} in a \textbf{stateless application}, securing \textbf{API endpoints} with \textbf{custom filters} and configuring \textbf{CORS} for \textbf{frontend integration}.}
 

            
          \resumeItemListEnd

     \resumeProjectHeading{\textbf{Web Journal - A Journal for Software Developers} $|$ \emph{HTML, CSS, Javascript, Electron.js, Puppeteer}}

    \resumeItemListStart
    \resumeItem{Collaborated with a team of 10 fellow students to build a desktop application designed to help developers efficiently track their work and goals.}
\resumeItem{Leveraged \textbf{Electron.js} to ensure compatibility across Windows, MacOS, and Linux without internet connection.}
\resumeItem{Designed features such as a fully navigable \textbf{calendar} with major holidays, a \textbf{markdown-supported notes page}, a \textbf{to-do list} for long-term goal tracking, and a \textbf{labeling system} for efficient work organization.}
\resumeItem{Wrote test cases using puppeteer to ensure the best user experience}

    \resumeItemListEnd
    

         \resumeProjectHeading{\textbf{AI Chatbot for Real-Time Stock Market Data} $|$ \emph{Next.js, Tailwind CSS, Javascript, Java, SpringBoot}}

    \resumeItemListStart
\resumeItem{Architected a real-tiome AI chatbot Using \textbf{Gemini AI} and \textbf{Alpha Vantage API} for stock market, giving users access to the most recent financial insights.
}
\resumeItem{To manage API requests, set up a \textbf{Spring Boot} as the backend.
}
\resumeItem{Built a \textbf{responsive frontend} with \textbf{Next.js} and used \textbf{Tailwind CSS} for styling, utilized  \textbf{TS Particles} to enhance user experience. }
\resumeItem{Deployed the application for live use, enabling access to stock market data through a polished and interactive interface.}

    \resumeItemListEnd
    

    

    

%-----------Experience---------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Help Desk Assistant}{June 2024-September 2024}
      {}{Phoenix, AZ}
       \resumeItemListStart
            \resumeItem{ Provided technical support for over 70-room motel, managing check-in/out software, troubleshooting hardware/software issues, and ensuring smooth operation of front desk systems. }
            \resumeItem{Helped in training staff on computer systems, resolving IT-related queries, and maintaining secure, efficient network connectivity for both staff and guest use.}
            
      
      \resumeItemListEnd


%-----------PROGRAMMING SKILLS-----------

\section{Skills and Technologies}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: C++, Java, JavaScript, Python, HTML} \\
     \textbf{Developer Tools}{: Git, GitHub, } \\
     \textbf{Libraries}{: SpringBoot, React.js, Next.js, Tailwind CSS}
    }}
 \end{itemize}


%-------------------------------------------
\end{document}
